PK object batch mode trial

### 2023-07-11 data-raw/batchMode_trial_gpm.Rmd
Updated methods to work for full cvt data and ensure that Rblood2plasma was accurately passed onto coefs()

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                              "DTXSID5032600"))

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID3061635"))

@@

```{r single_fit}
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

@@

```{r after_method_update}
# Changed pk_methods coef() and predict() to those above
# Ran the following after making the pk object:
devtools::load_all()

@@

```{r remaining_methods}
# coef_sd
# logLik.pk

devtools::load_all()
AIC(my_pk)
BIC(my_pk)

@@

```{r for_loop_allDTXSIDs}

# All DTXSID
eachDTXSID <- unique(cvt$chemicals_analyzed.dsstox_substance_id)

id <- 1
AIC_BIC <- data.frame()
while (id <= 10) {
  # Establishing the loop
  DTX_set <- eachDTXSID[seq(from = id, to = id + 3)]
  DTX_set <- DTX_set[!is.na(DTX_set)]
  print(DTX_set)
  id <- id + 4
  Sys.sleep(0.5)

  # Subsetting cvt
  my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% DTX_set)

  # Fitting loop
  my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species)) # Pooled model

  my_pk <- do_fit(my_pk)

  # OUTPUTS
  # AIC/BIC
  temp_AIC <- AIC(my_pk)
  temp_BIC <- BIC(my_pk)
  temp_IC <- left_join(temp_AIC, temp_BIC)
  AIC_BIC <- bind_rows(AIC_BIC, temp_IC)

} # Doesn't work because something for Solvent red 1 introduces an error

>>>>

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                              "DTXSID5032600",
                                                              "DTXSID2021103"))
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID5032600")

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID2021103")
# Opt params not found ERROR
# 
#

@@

```{r single_fit}
my_pk <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

@@

```{r after_method_update}
# Changed pk_methods coef() and predict() to those above
# Ran the following after making the pk object:
devtools::load_all()
all_my_data <- my_pk$data # following the full dataset to prefit
my_pk$data %>% filter(Chemical == "DTXSID2021103")

@@

```{r remaining_methods}
# coef_sd

devtools::load_all()
AIC(my_pk2) %>% View()
BIC(my_pk)

@@

```{r allDTXSIDs_analysis}

# after fitting pk object for all cvt objects
# saveRDS(my_pk, file = "data-raw/all_cvt_pk.rds")

my_tkstats <- get_tkstats(my_pk)
my_IC <- left_join(AIC(my_pk), BIC(my_pk))

my_IC %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "bobyqa") %>%
  ungroup() %>%
  count(model)
# model_1comp 60
# model_2comp 48
# model_flat   3

my_IC %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "L-BFGS-B") %>% View()
  ungroup() %>%
  count(model)
# model_1comp 56
# model_2comp 50
# model_flat   5

all_my_data <- my_pk$data
